Preparing for Potential Closure of European Airspaces due to Re-entering Space Objects

### 2025-05-05 paper.qmd
Update paper.qmd

The modelling and tracking of uncontrolled re-entries poses challenges.
Actual and historic data is sparse, and the size, shape, and attitude or
rotation of re-entering objects increase the level of uncertainty for
modelling. Common approaches employ a mix of handling the uncertainty of
object or debris movement, the associated exposed area, including
temporal uncertainty windows.

```         
  <!-- is there more to say and provide context? -->
```

>>>>

The modelling and tracking of uncontrolled re-entries poses challenges in terms of safety awareness and operational risk.
Actual and historic data is sparse, and the size, shape, and attitude or
rotation of re-entering objects increase the level of uncertainty for
modelling. To support the decision-making, common approaches employ a mix of handling the uncertainty of
object or debris movement and the associated exposed area for encounter, including
temporal uncertainty windows.
Thus, computationally efficient methods to assess and continously revalidate the collision risk of uncontrolled re-entries and aircraft will help to fine-tune the decision-making and geo-spactial and temporal constraints on aviation.
```         
  <!-- is there more to say and provide context? -->
```
